Outputs - civil servants' survey

### 2024-12-05 reports/paper_outputs_Dec_2024.qmd
Update paper_outputs_Dec_2024.qmd

```{r}
#source("Operationalization_31.7.R")

@@

1-factor model
```{r}
cfa.model.1factor <-
  'one_factor =~ Q4_1+ Q4_2+ Q4_3 + Q10_1+ Q10_2+ Q10_3 + PAST_EFFORT + Q22_1+ Q22_2+ Q22_3 + Q15+ Q16_1+ Q16_2+ Q16_3+ Q16_4+ Q16_5 + PROJECT_POLITICIZATION + PROJECT_INFLUENCE'

@@

>>>>

```{r}
#source("C:\\Users\\nirko\\Dropbox\\Civil Servants' Perceptions of Democratic Decline\\Code\\Operationalization & CFA\\Operationalization.R")
#source("C:\\Users\\nirko\\Dropbox\\Civil Servants' Perceptions of Democratic Decline\\Code\\Operationalization & CFA\\Weights.R")

@@

1-factor model
```{r}
#filter data
data_for_analysis_senior <- new_data %>% 
  filter((ranking !="junior") %>% replace_na(TRUE)) %>% 
  filter(INTENT_EXIT_2>0|
           PROJECT_EFFORT>0|
           PROJECT_VOICE>0)

cfa.model.1factor <-
  'one_factor =~ Q4_1+ Q4_2+ Q4_3 + Q10_1+ Q10_2+ Q10_3 + PAST_EFFORT + Q22_1+ Q22_2+ Q22_3 + Q15+ Q16_1+ Q16_2+ Q16_3+ Q16_4+ Q16_5 + PROJECT_POLITICIZATION + PROJECT_INFLUENCE'

@@

Model for exit, voice and work - weighted
```{r}

# Merge the dataset with weights with the data_for_analysis_senior based on ResponseId and add the combined_weight column
data_for_analysis_senior <- merge(data_for_analysis_senior, 
                                   data_for_analysis_with_weights[, c("ResponseId", "combined_weight")], 
                                   by = "ResponseId", 
                                   all.x = TRUE)

# standardize weight
data_for_analysis_senior$standardized_weight <- as.numeric(data_for_analysis_senior$combined_weight / mean(data_for_analysis_senior$combined_weight, na.rm = TRUE))

exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
            data=data_for_analysis_senior,
            weights = standardized_weight)
exit_mod2 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
exit_mod3 <- exit_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
exit_mod4 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
